---
title: "stl_lead_steven"
author: "Steven Cognac"
date: "8/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(skimr)

```

## Read .csv file stl_blood_lead.csv

```{r}
stl_blood <- read_delim(here::here("data", "data-raw", "stl_blood_lead.csv"), delim = ";") %>% 
  clean_names() %>% 
  mutate() %>% 
  mutate(pct_elevated = str_replace(pct_elevated,
                                   patter = ",",
                                   replacement = ".")) %>% 
  mutate(pct_elevated = as.numeric(pct_elevated))

```
## View the details of the project in skimr
```{r}
skimr::skim(stl_blood)

```

## Create scatterplot and graph percentage of childeren in each census tract with elevated blood lead levels vs the percent of each census tract identifying as white
```{r}

stl_lead_plot <- ggplot(data = stl_blood, (aes(x = white, y = pct_elevated))) +
  geom_point(aes(color = pct_elevated, alpha = 0.4)) +
  theme_minimal() +
  labs(x = "Total White Population",
       y = "% Elevated",
       title = "High Blood Lead Levels in White Population\n in St. Louis, Missouri")
  


stl_lead_plot

```
## save the plot as a .png
```{r}
ggsave(here::here("figs", "stl_lead_plot.png"), width = 6, height = 5)

```

#### The graph represents the percent of elevated lead levels compared to the total white population in St. Louis, Missouri. The general trend shows  


## Create histogram of pct_elevated
```{r}
stl_histo_plot <- ggplot(data = stl_blood, aes(x = pct_elevated)) +
  geom_histogram(fill="lightblue",color="red", linetype="dashed", alpha = 0.5) +
  labs(x = "% Elevated",
       title = "Histogram of % Elevated")

stl_histo_plot

```
## Export to figs folder
```{r}
ggsave(here::here("figs", "stl_histo_plot.jpg"), width = 6, height = 5)

```

